week getbackontrack

### 2024-10-31 weekbacktrack.Rmd
panicadded

>>>>

## ACTUAL Timeline

deadline: Saturday, 23.11.24

+---------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+:============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:=========================================================+
| ![](images/used_arson%20frog.jpg)                                                           | ![](images/used_arson%20frog.jpg){width="952"}             | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking_meh.jpg){width="800"}Plotting                 | ![](images/timetopanic.gif){width="800"}[chores at home] |
|                                                                                             |                                                            | [Asked Jochem for input]                                      |                                                                                            | Clarify [D] & define data [S1]\                                 |                                                                           |                                                          |
|                                                                                             |                                                            |                                                               | Outline Intro and theory [W]                                                               | & create effects structure [S2]                                 | Revisit RQs [D]                                                           |                                                          |
|                                                                                             |                                                            |                                                               | Clarify [D] & define data [S1]                                                             |                                                                 |                                                                           |                                                          |
+---------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
| ![](images/socialnetworking_meh.jpg){width="800"}\                                          | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}Specify model [S4]           | ![](images/timetopanic.gif){width="800"}[Grandmas bday]  |
| Plotting                                                                                    |                                                            |                                                               | Initial description [S3]                                                                   | rewrite intro and Theory [W]                                    |                                                                           |                                                          |
|                                                                                             |                                                            |                                                               |                                                                                            |                                                                 | Plotting                                                                  |                                                          |
|                                                                                             |                                                            |                                                               | Revisit RQs                                                                                |                                                                 |                                                                           |                                                          |
+---------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
| ![](images/socialnetworking_meh.jpg){width="800"}                                           | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                             |
| Data & methods part [W]                                                                     |                                                            |                                                               |                                                                                            | Plotting                                                        | Start Results [W]                                                         | [chores at home and university]                          |
+---------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
| ![](images/used_arson frog.jpg)[Research project course starts: little time to work on SNA] | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}Results [W]                               | ![](images/socialnetworking.jpg){width="800"}Finish Results [W] | ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]  |                                                          |
|                                                                                             |                                                            |                                                               |                                                                                            | Discussion & conclusion [W]                                     | ![](images/kermit-panic.gif){width="500"}Format project website& hand in! |                                                          |
+---------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+

::: columns
::: {.column width="50%"}
![social network plot (color) = time for SNA (obvious... or not?)](images/socialnetworking.jpg){alt="social network plot (color) = time for SNA (obvious... or not?)" width="80"}

![social network plot (muted) = not a lot of time for SNA, but SOME](images/socialnetworking_meh.jpg){alt="social network plot (muted) = not a lot of time for SNA, but SOME" width="80"}

![arson = otherwise busy/NO time for SNA](images/used_arson%20frog.jpg){alt="arson = otherwise busy/NO time for SNA" width="80"}
:::

::: {.column width="50%"}
![time to panic = chores, admin work, and mental breakdowns/ NO time for SNA](images/timetopanic.gif){width="80"}

![kermit panicking = self-explanatory](images/kermit-panic.gif){width="80"}
:::
:::
